---
title: "p8130_final_project"
author: "Senna"
date: "2024-12-14"
output: html_document
---

```{r}
library(tidyverse)
library(ResourceSelection)
library(car)

```

```{r}
# read data file and check if there is a missing value
surv_data = read_csv("Project_2_data.csv")

any(is.na(surv_data)) # FALSE

# check all vairiables' info
summary(surv_data)

```

```{r}
surv_data = surv_data |>
  janitor::clean_names() |>
  rename(regional_node_positive = reginol_node_positive) |>
  mutate(
    positive_ratio = regional_node_positive/regional_node_examined,
    status = ifelse(status == "Alive", 0, 1),
    estrogen_status = ifelse(estrogen_status == "Positive", 1,0),
    progesterone_status = ifelse(progesterone_status == "Positive", 1,0)
  )|>
  mutate(across(where(is.character), as.factor))


head(surv_data)
```

# Trying Cox Proportional Hazards Model
```{r}
# Load survival package
library(survival)

# Fit a Cox proportional hazards model
cox_model <- coxph(Surv(survival_months, status) ~ age + race + marital_status + t_stage + n_stage + x6th_stage + differentiate + grade + a_stage + tumor_size + estrogen_status + progesterone_status + regional_node_examined + regional_node_positive, data = surv_data)

# View model summary
summary(cox_model)
```

NA coefficients; colliearity? -->
remove these variables: x6th stage, grade

```{r}
cox_2<- coxph(Surv(survival_months, status) ~ age + race + marital_status + t_stage + n_stage  + differentiate + a_stage + tumor_size + estrogen_status + progesterone_status + regional_node_examined + regional_node_positive, data = surv_data)

# View model summary
summary(cox_2)
```



# assess performance of the model

concordance index : The C-index ranges from 0.5 (no better than random chance) to 1 (perfect discrimination). A higher C-index indicates better model performance.
```{r}
surv_object <- Surv(surv_data$survival_months, surv_data$status)

# Compute the concordance index
concordance.index <- survConcordance(surv_object ~ predict(cox_2, type = "risk"), data = surv_data)

# Print the concordance index
print(concordance.index)

```
0.744: acceptable discrimination. In 74% of the cases, the model correctly ranks pairs of individuals in terms of who experiences the event sooner


# Assumptions:
1. Proportional Hazards Assumption
The core assumption of the Cox model is that the hazard ratios between groups are constant over time. This means that the effect of the covariates on the hazard rate is proportional and does not change over time. To check for this assumption:

Use statistical tests like Schoenfeld residuals test.
Plot the scaled Schoenfeld residuals for each covariate over time.

More conditions to be met for optimal performance of the model
## linearity of continuous variables, independence of survival terms, no time varying covariates, minimal ties (when two or more individuals experience the event at the same time), no extreme outliers or influential points, balanced data, no multicollinearity


1. Check proportional hazards assumptions with the Schoenfeld Residuals test
```{r}
# Test for proportional hazards assumption using Schoenfeld residuals
ph_test <- cox.zph(cox_2)

# Display test results
print(ph_test)
```
P values for a covariate < 0.5 --> suggests a violation of the proportion hazards assumption for that covariate. 

** n_stage, a_stage, tumor_size, estrogen_status, progesterone status have p values smaller than 0.5. Should we exclude these? 

If the residuals show a random scatter with no clear trend or pattern, it suggests that the proportional hazards assumption holds.
If there is a visible pattern or trend, it indicates that the assumption might be violated for that covariate.

# Residual Analysis: helps indentify influential data points, outliers, or poor fit in the model

Martingale residuals: Can be used to assess the fit of the model. A plot of martingale residuals against covariates should show no clear pattern.
Deviance residuals: These are useful for detecting outliers.
Schoenfeld residuals: Used for checking the proportional hazards assumption.

```{r}
# Martingale residuals plot
martingale_residuals <- residuals(cox_2, type = "martingale")
plot(martingale_residuals, main = "Martingale Residuals", ylab = "Residuals")


# Deviance residuals plot
deviance_residuals <- residuals(cox_2, type = "deviance")
plot(deviance_residuals, main = "Deviance Residuals", ylab = "Residuals")

# relationship between residuals and covariates
plot(surv_data$n_stage, martingale_residuals, main = "Martingale Residuals vs covariate", 
     xlab = "covariate", ylab = "Martingale Residuals")

plot(surv_data$a_stage, martingale_residuals, main = "Martingale Residuals vs covariate", 
     xlab = "covariate", ylab = "Martingale Residuals")

plot(surv_data$tumor_size, martingale_residuals, main = "Martingale Residuals vs covariate", 
     xlab = "covariate", ylab = "Martingale Residuals")

plot(surv_data$estrogen_status, martingale_residuals, main = "Martingale Residuals vs covariate", 
     xlab = "covariate", ylab = "Martingale Residuals")

plot(surv_data$progesterone_status, martingale_residuals, main = "Martingale Residuals vs covariate", 
     xlab = "covariate", ylab = "Martingale Residuals")
```

Those variables could be time varying

```{r}
cox_3 <- coxph(Surv(survival_months, status) ~ age + race + marital_status +
               tt(n_stage) + tt(a_stage) + tt(tumor_size) + estrogen_status + 
               progesterone_status + regional_node_examined + regional_node_positive, 
               data = surv_data, 
               tt = function(x, t, ...) x * log(t)) 
## data contains an infinite predictor????
```

# influential points and leverage
Use influence diagnostics (e.g., dfbetas, deviance residuals, or Cook's distance) to identify outliers or influential points.

You can assess influential points using dfbeta (influence on regression coefficients) and dffit (influence on fitted values). These can be plotted to check for any data points that have a large effect on the model.
```{r}
# Compute DFBETAs
dfbeta_values <- residuals(cox_2, type = "dfbeta")

# View the DFBETAs for each predictor
head(dfbeta_values)
```


# check for multicollinearity
Multicollinearity between predictors can affect the stability of the model. You can assess this using the variance inflation factor (VIF).
```{r}
library(car)

# Compute condition index and variance decomposition proportions
collinearity <- vif(cox_2, tol = TRUE)
print(collinearity)
```

VIF (Variance Inflation Factor) measures how much the variance of the estimated regression coefficients is inflated due to collinearity with other predictors in the model.
A VIF value of 1 indicates no collinearity for a particular predictor, meaning that the predictor is not correlated with other predictors.
A VIF value greater than 1 indicates the presence of collinearity. As the value increases, it suggests stronger collinearity with other variables in the model.
VIF values above 5 or 10 are typically considered as indicators of high multicollinearity, meaning that the variable is highly correlated with other predictors. This could cause issues in interpreting the model, as it makes the coefficients unstable and increases the standard errors.


# cross validation
```{r}
library(survival)
library(caret)
train_control <- trainControl(method = "cv", number = 10)  # 10-fold cross-validation

```
 
#  Akaike Information Criterion (AIC) and Bayesian Information Criterion (BIC)
AIC and BIC are measures used to compare the relative fit of different models. Lower values of AIC and BIC indicate a better-fitting model, penalizing for adding too many variables.
```{r}


```


Assumption is violated. What next?
1. Stratify the model by violating covariates
2. if covariate's effect change over time, include it as time-varying covariate in the model. (create interaction term between covariate and time)
3. check for non linear effects. 

2. is very likely... prognosis ... 
chat gpt says:
Time-Varying: n_stage, x6th_stage, a_stage, and tumor_size could all vary over time as the disease progresses or responds to treatment. These would likely be treated as time-varying covariates in survival analysis.

Not Time-Varying: Estrogen_status and progesterone_status are generally fixed after diagnosis and do not change over time under typical circumstances, so they would not be treated as time-varying covariates.

