---
title: "model building"
author: "Elaine"
output: html_document
---

Import necessary libraries
```{r, message=FALSE}
library(dplyr)
library(funModeling)
library(MASS)
library(gridExtra)
library(tidyverse)
library(corrplot)
library(Hmisc)
library(survival)
library(survminer)
library(ggplot2)
library(ggpubr)
library(magrittr)
library(knitr)
library(rms)
library(foreign)
library(pROC)
library(timeROC)
```

## Data Processing
Import and clean the dataset
```{r, message=FALSE}
# read data file and check if there is a missing value
surv_data = read_csv("Project_2_data.csv")|>
  janitor::clean_names() |>
  rename(regional_node_positive = reginol_node_positive) |>
  mutate(
    positive_ratio = regional_node_positive/regional_node_examined,
    status = ifelse(status == "Alive", 0, 1)
      ) |>
  mutate(
    grade = case_when(
      grade == "1" ~ 1,
      grade == "2" ~ 2,
      grade == "3" ~ 3,
      grade == "anaplastic; Grade IV" ~ 4)) |>
  mutate(across(where(is.character), as.factor))|>
  relocate(status, survival_months, everything())

any(is.na(surv_data)) # FALSE

summary(surv_data) |>
  knitr::kable()
```
Checking the correlation between numerical variables
```{r}
cor_matrix = surv_data |>
  select_if(is.numeric) |>
  cor() 
corrplot::corrplot(cor_matrix, 
                   type = "upper",
                   diag = FALSE, 
                   addCoef.col = "black",
                   tl.col = "black",
                   tl.srt = 45)
```
The correlation matrix shows that the numerical variables in the dataset have low to moderate correlations with each other. The relatively higher correlation among `reginal_node_positive`, `reginal_node_examined`, and `positive_ratio` is expected. In the later analysis, we will only consider positive ratio for model building.

Check the correlation between categorical variables
```{r, warning=FALSE}

categorical_vars <- surv_data |>
  select_if(is.factor)

association_test <- function(var1, var2) {
  
  cont_table <- table(var1, var2)
  chi_test <- chisq.test(cont_table)
  n <- sum(cont_table)
  min_dim <- min(dim(cont_table)) - 1
  cramer_v <- sqrt(chi_test$statistic / (n * min_dim))
  
  return(list(
    chi_square = chi_test$statistic,
    p_value = chi_test$p.value,
    cramer_v = cramer_v
  ))
}

results <- list()
var_names <- names(categorical_vars)
for(i in 1:(length(var_names)-1)) {
  for(j in (i+1):length(var_names)) {
    var1 <- var_names[i]
    var2 <- var_names[j]
    
    test_result <- association_test(
      categorical_vars[[var1]], 
      categorical_vars[[var2]]
    )
    
    results[[paste(var1, var2, sep="-")]] <- c(
      test_result,
      list(var1 = var1, var2 = var2)
    )
  }
}

results_df <- do.call(rbind, lapply(results, function(x) {
  data.frame(
    Variable1 = x$var1,
    Variable2 = x$var2,
    Chi_Square = x$chi_square,
    P_Value = x$p_value,
    Cramers_V = x$cramer_v
  )
})) |>
  arrange(P_Value)

kable(results_df, 
      digits = 4,
      col.names = c("var1", "var2", "chi-statistic", "P-value", "Cramer's V"))
```
The correlation analysis of categorical variables in this breast cancer dataset reveals several key patterns. The strongest associations are found between staging-related variables, with differentiate-grade showing perfect correlation (Cramer's V = 1.0) and n_stage-x6th_stage displaying very strong correlation (Cramer's V = 0.91). A notable moderate correlation exists between hormone receptor statuses (estrogen_status-progesterone_status, Cramer's V = 0.51), which aligns with biological understanding. While many other associations are statistically significant (p < 0.05), their weaker Cramer's V values (< 0.3) suggest limited practical significance. 

Check the distribution of numerical variables
```{r}
surv_data |>
  funModeling::plot_num()
```
Box-Cox transformation
```{r}
surv_data = surv_data |>
  mutate(
      positive_ratio_transformed = {
      bc = boxcox(positive_ratio ~ 1, plotit = FALSE)
      lambda = bc$x[which.max(bc$y)]
      if(abs(lambda) < 1e-4) {
        log(positive_ratio)
      } else {
        (positive_ratio^lambda - 1) / lambda
      }
    }
  )
```

```{r}
p1 <- ggplot(surv_data, aes(x = positive_ratio)) +
  geom_histogram(fill = "skyblue", bins = 30) +
  labs(title = "Original Distribution",
       x = "Positive Ratio")

p2 <- ggplot(surv_data, aes(x = positive_ratio_transformed)) +
  geom_histogram(fill = "lightgreen", bins = 30) +
  labs(title = "Transformed Distribution",
       x = "Transformed Positive Ratio")

grid.arrange(p1, p2, ncol = 2)
```
## Model Building

### Kaplan-Meier Survival Analysis
```{r}
survfit(Surv(survival_months,status)~race,data = surv_data) |> 
  ggsurvplot(
    size = 1,
    cex.lab= 2,
    break.time.by = 6,
    xlim = c(0,107),
    axis.title.x =element_text(size=5), 
    axis.title.y = element_text(size=5),
    palette = c("#54A136", "#C757A0", "#3291ca"),
    conf.int = TRUE,
    pval = TRUE,
    risk.table = TRUE,
    xlab = "Follow-up months", 
    ylab="Survival probability ",
    risk.table.col = "strata",
    risk.table.fontsize = 3, 
    legend.labs =  c("White", "Black", "Other" ),
    risk.table.height = 0.3, 
    ggtheme = theme_bw()
    )
```
```{r}
survfit(Surv(survival_months,status)~marital_status,data = surv_data) |> 
  ggsurvplot(
    size = 1,
    cex.lab= 2,
    break.time.by = 6,
    xlim = c(0,107),
    axis.title.x =element_text(size=5), 
    axis.title.y = element_text(size=5),
    palette = c("#54A136", "#C757A0", "#3291ca", "#FFA500", "#FF0000"),
    conf.int = TRUE,
    pval = TRUE,
    risk.table = TRUE,
    xlab = "Follow-up months", 
    ylab="Survival probability ",
    risk.table.col = "strata",
    risk.table.fontsize = 3, 
    legend.labs =  c("Married", "Single", "Separated", "Divored", "Widowed"),
    risk.table.height = 0.3, 
    ggtheme = theme_bw()
    )
```
```{r}
survfit(Surv(survival_months,status)~t_stage,data = surv_data) |> 
  ggsurvplot(
    size = 1,
    cex.lab= 2,
    break.time.by = 6,
    xlim = c(0,107),
    axis.title.x =element_text(size=5), 
    axis.title.y = element_text(size=5),
    palette = c("#54A136", "#C757A0", "#3291ca", "#FFA500", "#FF0000"),
    conf.int = TRUE,
    pval = TRUE,
    risk.table = TRUE,
    xlab = "Follow-up months", 
    ylab="Survival probability ",
    risk.table.col = "strata",
    risk.table.fontsize = 3, 
    legend.labs =  c("T1", "T2", "T3", "T4"),
    risk.table.height = 0.3, 
    ggtheme = theme_bw()
    )
```

```{r}
survfit(Surv(survival_months,status)~n_stage,data = surv_data) |> 
  ggsurvplot(
    size = 1,
    cex.lab= 2,
    break.time.by = 6,
    xlim = c(0,107),
    axis.title.x =element_text(size=5), 
    axis.title.y = element_text(size=5),
    palette = c("#54A136", "#C757A0", "#3291ca"),
    conf.int = TRUE,
    pval = TRUE,
    risk.table = TRUE,
    xlab = "Follow-up months", 
    ylab="Survival probability ",
    risk.table.col = "strata",
    risk.table.fontsize = 3, 
    legend.labs =  c("N1", "N2", "N3"),
    risk.table.height = 0.3, 
    ggtheme = theme_bw()
    )
```

```{r}
survfit(Surv(survival_months,status)~x6th_stage,data = surv_data) |> 
  ggsurvplot(
    size = 1,
    cex.lab= 2,
    break.time.by = 6,
    xlim = c(0,107),
    axis.title.x =element_text(size=5), 
    axis.title.y = element_text(size=5),
    palette = c("#54A136", "#C757A0", "#3291ca", "#FFA500", "#FF0000"),
    conf.int = TRUE,
    pval = TRUE,
    risk.table = TRUE,
    xlab = "Follow-up months", 
    ylab="Survival probability ",
    risk.table.col = "strata",
    risk.table.fontsize = 3, 
    legend.labs =  c("IIA", "IIB", "IIIA","IIIB", "IIIC"),
    risk.table.height = 0.3, 
    ggtheme = theme_bw()
    )
```

```{r}
survfit(Surv(survival_months,status)~differentiate,data = surv_data) |> 
  ggsurvplot(
    size = 1,
    cex.lab= 2,
    break.time.by = 6,
    xlim = c(0,107),
    axis.title.x =element_text(size=5), 
    axis.title.y = element_text(size=5),
    palette = c("#54A136", "#C757A0", "#3291ca", "#FFA500"),
    conf.int = TRUE,
    pval = TRUE,
    risk.table = TRUE,
    xlab = "Follow-up months", 
    ylab="Survival probability ",
    risk.table.col = "strata",
    risk.table.fontsize = 3, 
    legend.labs =  c("Moderately differentiated", "Poorly differentiated", "Well differentiated", "Undifferentiated"),
    risk.table.height = 0.3, 
    ggtheme = theme_bw()
    )
```

```{r}
survfit(Surv(survival_months,status)~grade,data = surv_data) |> 
  ggsurvplot(
    size = 1,
    cex.lab= 2,
    break.time.by = 6,
    xlim = c(0,107),
    axis.title.x =element_text(size=5), 
    axis.title.y = element_text(size=5),
    palette = c("#54A136", "#C757A0", "#3291ca", "#FFA500"),
    conf.int = TRUE,
    pval = TRUE,
    risk.table = TRUE,
    xlab = "Follow-up months", 
    ylab="Survival probability ",
    risk.table.col = "strata",
    risk.table.fontsize = 3, 
    legend.labs =  c("1", "2", "3", "4"),
    risk.table.height = 0.3, 
    ggtheme = theme_bw()
    )
```

```{r}
survfit(Surv(survival_months,status)~a_stage,data = surv_data) |> 
  ggsurvplot(
    size = 1,
    cex.lab= 2,
    break.time.by = 6,
    xlim = c(0,107),
    axis.title.x =element_text(size=5), 
    axis.title.y = element_text(size=5),
    palette = c("#54A136", "#C757A0"),
    conf.int = TRUE,
    pval = TRUE,
    risk.table = TRUE,
    xlab = "Follow-up months", 
    ylab="Survival probability ",
    risk.table.col = "strata",
    risk.table.fontsize = 3, 
    legend.labs =  c("Distant","Regional"),
    risk.table.height = 0.3, 
    ggtheme = theme_bw()
    )
```

```{r}
survfit(Surv(survival_months,status)~estrogen_status,data = surv_data) |> 
  ggsurvplot(
    size = 1,
    cex.lab= 2,
    break.time.by = 6,
    xlim = c(0,107),
    axis.title.x =element_text(size=5), 
    axis.title.y = element_text(size=5),
    palette = c("#54A136", "#C757A0"),
    conf.int = TRUE,
    pval = TRUE,
    risk.table = TRUE,
    xlab = "Follow-up months", 
    ylab="Survival probability ",
    risk.table.col = "strata",
    risk.table.fontsize = 3, 
    legend.labs =  c("Positive","Negative"),
    risk.table.height = 0.3, 
    ggtheme = theme_bw()
    )
```

```{r, message=FALSE}
survfit(Surv(survival_months,status)~progesterone_status,data = surv_data) |> 
  ggsurvplot(
    size = 1,
    cex.lab= 2,
    break.time.by = 6,
    xlim = c(0,107),
    axis.title.x =element_text(size=5), 
    axis.title.y = element_text(size=5),
    palette = c("#54A136", "#C757A0"),
    conf.int = TRUE,
    pval = TRUE,
    risk.table = TRUE,
    xlab = "Follow-up months", 
    ylab="Survival probability ",
    risk.table.col = "strata",
    risk.table.fontsize = 3, 
    legend.labs =  c("Positive","Negative"),
    risk.table.height = 0.3, 
    ggtheme = theme_bw()
    )
```

```{r}
surv_data = surv_data |>
  mutate(age_group = ifelse(age > mean(age, na.rm = TRUE), "Elder", "Young"))

survfit(Surv(survival_months,status)~age_group,data = surv_data) |>
  ggsurvplot(
    size = 1,
    cex.lab= 2,
    break.time.by = 6,
    xlim = c(0,107),
    axis.title.x =element_text(size=5), 
    axis.title.y = element_text(size=5),
    palette = c("#54A136", "#C757A0"),
    conf.int = TRUE,
    pval = TRUE,
    risk.table = TRUE,
    xlab = "Follow-up months", 
    ylab="Survival probability ",
    risk.table.col = "strata",
    risk.table.fontsize = 3, 
    legend.labs =  c("Young","Elder"),
    risk.table.height = 0.3, 
    ggtheme = theme_bw()
    )
```

```{r}
surv_data <- surv_data |>
  mutate(tumor_size_group = case_when(
    tumor_size < 40 ~ "Small (<40)",
    tumor_size >= 40 & tumor_size < 80 ~ "Medium (40-80)",
    tumor_size >= 80 & tumor_size < 120 ~ "Large (80-120)",
    tumor_size >= 120 ~ "Very Large (>120)"
  ))

 survfit(Surv(survival_months,status)~tumor_size_group,data = surv_data) |>
  ggsurvplot(
    size = 1,
    cex.lab= 2,
    break.time.by = 6,
    xlim = c(0,107),
    axis.title.x =element_text(size=5), 
    axis.title.y = element_text(size=5),
    palette = c("#54A136", "#C757A0", "#3291ca", "#FFA500"),
    conf.int = TRUE,
    pval = TRUE,
    risk.table = TRUE,
    xlab = "Follow-up months", 
    ylab="Survival probability ",
    risk.table.col = "strata",
    risk.table.fontsize = 3, 
    legend.labs =  c("Small (<40)", "Medium (40-80)", "Large (80-120)", "Very Large (>120)"),
    risk.table.height = 0.3, 
    ggtheme = theme_bw()
    )
```

```{r}
surv_data <- surv_data |>
  mutate(positive_ratio_group = case_when(
    positive_ratio <= 0.25 ~ "Low (0.02-0.25)",
    positive_ratio > 0.25 & positive_ratio <= 0.5 ~ "Moderate (0.25-0.5)",
    positive_ratio > 0.5 & positive_ratio <= 0.75 ~ "High (0.5-0.75)",
    positive_ratio > 0.75 ~ "Very High (0.75-1)"
  ))

 survfit(Surv(survival_months,status)~positive_ratio_group,data = surv_data) |>
  ggsurvplot(
    size = 1,
    cex.lab= 2,
    break.time.by = 6,
    xlim = c(0,107),
    axis.title.x =element_text(size=5), 
    axis.title.y = element_text(size=5),
    palette = c("#54A136", "#C757A0", "#3291ca", "#FFA500"),
    conf.int = TRUE,
    pval = TRUE,
    risk.table = TRUE,
    xlab = "Follow-up months", 
    ylab="Survival probability ",
    risk.table.col = "strata",
    risk.table.fontsize = 3, 
    legend.labs =  c("Low (0.02-0.25)", "Moderate (0.25-0.5)", "High (0.5-0.75)", "Very High (0.75-1)"),
    risk.table.height = 0.3, 
    ggtheme = theme_bw()
    )
```
- All the Kaplan-Meier survival analyses show significant differences in survival probabilities among different groups of each variable.[ Log-rank test: p-value < 0.05]

## Univariate Cox Regression Model

\( h(t) = h_0(t) \exp(\beta_1 X) \)

```{r}
surv_object <- with(surv_data, Surv(survival_months, status))

result_unicox <- data.frame("Variable" = character(),
                     "Hazard Ratio" = numeric(),
                     "95%CI" = character(),
                     "P value" = numeric())

for (variable in c("age", "race", "marital_status", "t_stage", "n_stage", "x6th_stage", "differentiate", "grade", "a_stage", "tumor_size", "estrogen_status", "progesterone_status", "positive_ratio_transformed")) {
  cox_formula <- as.formula(paste("surv_object ~", variable))
  cox_model <- coxph(cox_formula, data = surv_data)
  
  variable_name <- variable
  hazard_ratio <- exp(coef(cox_model))
  ci_lower <- exp(confint(cox_model))[1]
  ci_upper <- exp(confint(cox_model))[2]
  p_value <- summary(cox_model)$coefficients[5]
  
  new_row <- data.frame("Variable" = variable_name,
                        "Hazard Ratio" = hazard_ratio,
                        "95% CI" = paste0("(", round(ci_lower, 2), "-", round(ci_upper, 2), ")"),
                        "P value" = p_value,
                        stringsAsFactors = FALSE)
  
  result_unicox <- rbind(result_unicox, new_row)
}

result_unicox = result_unicox |>
  arrange(desc(`P.value`))


knitr::kable(result_unicox, 
             col.names = c("Variable", "Hazard Ratio", "95% CI", "P value"))
```

According to the univariate Cox regression analysis, the variables `age,` `a_stage,` `tumor_size,` `grade,` `progesterone_status,` `estrogen_status,` and `positive_ratio`are significantly associated with the survival outcome (p < 0.05).

## Multivariate Cox Regression Model

```{r}
result_use = result_unicox |>
mutate(
  significant = ifelse(result_unicox$P.value < 0.05,"significant","Not significant"))

multi_cox <- result_use[result_use$significant == "significant",]$Variable

formula <- as.formula(paste("Surv(survival_months, status) ~", paste(multi_cox, collapse = " + ")))

multi_cox_model <- coxph(formula, data = surv_data)

data_use <- summary(multi_cox_model)

multi_cox_HR <- round(data_use$coefficients[,2],2)
multi_cox_CI2.5 <- round(data_use$conf.int[,3],2)
multi_cox_CI97.5 <- mul_CI95<-round(data_use$conf.int[,4],2)
multi_cox_CI <- paste0('(',multi_cox_CI2.5,'-',multi_cox_CI97.5,')')
multi_cox_P_value <- round(data_use$coefficients[,5],3)
Variable <- row.names(data.frame(data_use$coefficients))
multi_cox_result<- data.frame(Variable,multi_cox_HR,multi_cox_CI2.5,multi_cox_CI97.5,multi_cox_CI,multi_cox_P_value)

knitr::kable(multi_cox_result)
```

```{r}
ggplot(multi_cox_result, aes(multi_cox_HR, Variable)) + 
  geom_vline(xintercept = 1,
             linetype = "dashed",
             size = 1) +
  geom_errorbar(aes(xmin = multi_cox_CI2.5, xmax = multi_cox_CI97.5),width = 0.1) +
  geom_point(aes(color = multi_cox_P_value),size = 5, shape = 18) +
  scale_color_continuous(low = 'skyblue', high = 'red') +
  labs(x = 'Hazard ratio', title = 'Forest plot for multivariate cox regression') +
  theme_pubr() +
  theme(legend.position = 'right')
```
According to the multivariate Cox regression analysis, the variables `age,` `a_stage,` `tumor_size,` `grade,` `progesterone_status,` `estrogen_status,` and `positive_ratio` are significantly associated with the survival outcome (p < 0.05).

## Nomogram for Survival Prediction

```{r, warning=FALSE}
dd <- datadist(surv_data)
options(datadist = "dd")

surv_data = surv_data %>%
  mutate(survival_years = survival_months / 12)

surv_object <- with(surv_data, Surv(survival_years, status == 1))

final_model <- cph(surv_object ~ age + a_stage + tumor_size + grade + progesterone_status + estrogen_status + positive_ratio,
                   x = TRUE ,y = TRUE, surv = TRUE, data = surv_data)

surv =  Survival(final_model)

surv_1y <- function(x)surv(1,lp=x)
surv_4y <- function(x)surv(4,lp=x)
surv_8y <- function(x)surv(8,lp=x)

Nomogram_1 <- nomogram(final_model,fun = list(surv_1y,surv_4y,surv_8y),lp=F,
                       funlabel = c('1 year survival rate','4 year survival rate','8 year survival rate'),
                       maxscale = 100,fun.at = c(0.1,seq(0.1,0.9,by=0.1),0.90))

plot(Nomogram_1, 
     cex.axis = 0.4,
     cex.var = 0.8,
     cex = 0.8, 
     lmgp = 0.3,            # 减小标签与轴线距离
     label.offset = 0.2,    # 增加标签偏移量
     points.label = "Points",
     total.points.label = "Total Points",
     col.grid = gray(c(0.8, 0.95)),
     labels.right = FALSE,
     width.max = 1000,
     height.max = 800,
     mar = c(4, 4, 4, 4)    # 增加边距
)
```
## ROC curve
```{r, warning=FALSE}
pred <- predict(final_model, type="lp")

ROC_table <- data.frame(time = surv_data[,"survival_years"], status = surv_data[,"status"], score = pred)

time_roc_res <- timeROC(T = ROC_table$survival_years,
                        delta = ROC_table$status,
                        marker = ROC_table$score,
                        cause = 1,
                        weighting="marginal",
                        times = c(1, 4, 8),
                        ROC = TRUE,
                        iid = TRUE
                        )

time_ROC_df <- data.frame(TP_1year = time_roc_res$TP[, 1],
                          FP_1year = time_roc_res$FP[, 1],
                          TP_4year = time_roc_res$TP[, 2],
                          FP_4year = time_roc_res$FP[, 2],
                          TP_8year = time_roc_res$TP[, 3],
                          FP_8year = time_roc_res$FP[, 3]
                          )

ggplot(data = time_ROC_df) +
  geom_line(aes(x = FP_1year, y = TP_1year), size = 1, color = "#0067B5") +
  geom_line(aes(x = FP_4year, y = TP_4year), size = 1, color = "#09891D") +
  geom_line(aes(x = FP_8year, y = TP_8year), size = 1, color = "#BC1328") +
  geom_abline(slope = 1, intercept = 0, color = "grey", size = 1, linetype = 2) +
  theme_bw() +
  annotate("text",x = 0.75, y = 0.20, size = 4.5,label = paste0("AUC of 1-year survival = ", sprintf("%.3f", time_roc_res$AUC[[1]])), color = "#0067B5") +
  annotate("text",x = 0.75, y = 0.15, size = 4.5,label = paste0("AUC of 4-year survival = ", sprintf("%.3f", time_roc_res$AUC[[2]])), color = "#09891D") +
  annotate("text",x = 0.75, y = 0.10, size = 4.5,label = paste0("AUC of 8-year survival = ", sprintf("%.3f", time_roc_res$AUC[[3]])), color = "#BC1328") +
  labs(x = "1-specificity", y = "Sensitivity") +
  theme(axis.text = element_text(face = "bold", size = 11, color = "black"),
        axis.title.x = element_text(face = "bold", size = 14, color = "black", margin = margin(c(15, 0, 0, 0))),
        axis.title.y = element_text(face = "bold", size = 14, color = "black", margin = margin(c(0, 15, 0, 0))))
```


```{r, wearning=FALSE}
model_1 <- cph(surv_object ~ age + a_stage + tumor_size + grade + progesterone_status + estrogen_status + positive_ratio,
                   x = TRUE ,y = TRUE, surv = TRUE, time.inc = 1, data = surv_data)

cal_1 <- calibrate(model_1,
                   cmethod = 'KM',
                   method = 'boot',
                   u = 1,
                   B = 1000)

plot(cal_1,
     lwd = 2,
     lty = 1,
     errbar.col="blue",
     xlab="Nomogram-Predicted Probabilityof 1 years OS",
     ylab="Actua1 1 years OS",
     col="red",
     subtitles=F
     )

abline(0, 1, lty = 2, col = "gray")
```


```{r, warning=FALSE}
model_2 <- cph(surv_object ~ age + a_stage + tumor_size + grade + progesterone_status + estrogen_status + positive_ratio,
                   x = TRUE ,y = TRUE, surv = TRUE, time.inc = 4, data = surv_data)

cal_2 <- calibrate(model_1,
                   cmethod = 'KM',
                   method = 'boot',
                   u = 4,
                   B = 1000)

plot(cal_2,
     lwd = 2,
     lty = 1,
     errbar.col="blue",
     xlab="Nomogram-Predicted Probabilityof 1 years OS",
     ylab="Actua1 1 years OS",
     col="red",
     subtitles=F
     )

abline(0, 1, lty = 2, col = "gray")
```
```{r, warning=FALSE}
model_3 <- cph(surv_object ~ age + a_stage + tumor_size + grade + progesterone_status + estrogen_status + positive_ratio,
                   x = TRUE ,y = TRUE, surv = TRUE, time.inc = 8, data = surv_data)

cal_3 <- calibrate(model_1,
                   cmethod = 'KM',
                   method = 'boot',
                   u = 8,
                   B = 1000)

plot(cal_3,
     lwd = 2,
     lty = 1,
     errbar.col="blue",
     xlab="Nomogram-Predicted Probabilityof 1 years OS",
     ylab="Actua1 1 years OS",
     col="red",
     subtitles=F
     )

abline(0, 1, lty = 2, col = "gray")
```

