---
title: "model building"
author: "Elaine"
output: html_document
---

Import necessary libraries
```{r, message=FALSE}
library(dplyr)
library(funModeling)
library(MASS)
library(gridExtra)
library(tidyverse)
library(corrplot)
library(Hmisc)
library(survival)
library(survminer)
library(ggplot2)
library(ggpubr)
library(magrittr)
library(knitr)
library(rms)
library(foreign)
library(pROC)
library(timeROC)
```

## Data Processing

Import and clean the dataset
```{r, message=FALSE}
# read data file and check if there is a missing value
surv_data = read_csv("Project_2_data.csv")|>
  janitor::clean_names() |>
  rename(regional_node_positive = reginol_node_positive) |>
  mutate(
    positive_ratio = regional_node_positive/regional_node_examined,
    status = ifelse(status == "Alive", 0, 1)
      ) |>
  mutate(
    grade = case_when(
      grade == "1" ~ 1,
      grade == "2" ~ 2,
      grade == "3" ~ 3,
      grade == "anaplastic; Grade IV" ~ 4)) |>
  mutate(across(where(is.character), as.factor))|>
  relocate(status, survival_months, everything())

any(is.na(surv_data)) # FALSE

summary(surv_data) |>
  knitr::kable()
```

#### Checking the correlation between numerical variables
```{r}
cor_matrix = surv_data |>
  select_if(is.numeric) |>
  cor() 
corrplot::corrplot(cor_matrix, 
                   type = "upper",
                   diag = FALSE, 
                   addCoef.col = "black",
                   tl.col = "black",
                   tl.srt = 45)
```

The correlation matrix shows that the numerical variables in the dataset have low to moderate correlations with each other. The relatively higher correlation among `reginal_node_positive`, `reginal_node_examined`, and `positive_ratio` is expected. In the later analysis, we will only consider positive ratio for model building.

#### Check the correlation between categorical variables
```{r, warning=FALSE}

categorical_vars <- surv_data |>
  select_if(is.factor)

association_test <- function(var1, var2) {
  
  cont_table <- table(var1, var2)
  chi_test <- chisq.test(cont_table)
  n <- sum(cont_table)
  min_dim <- min(dim(cont_table)) - 1
  cramer_v <- sqrt(chi_test$statistic / (n * min_dim))
  
  return(list(
    chi_square = chi_test$statistic,
    p_value = chi_test$p.value,
    cramer_v = cramer_v
  ))
}

results <- list()
var_names <- names(categorical_vars)
for(i in 1:(length(var_names)-1)) {
  for(j in (i+1):length(var_names)) {
    var1 <- var_names[i]
    var2 <- var_names[j]
    
    test_result <- association_test(
      categorical_vars[[var1]], 
      categorical_vars[[var2]]
    )
    
    results[[paste(var1, var2, sep="-")]] <- c(
      test_result,
      list(var1 = var1, var2 = var2)
    )
  }
}

results_df <- do.call(rbind, lapply(results, function(x) {
  data.frame(
    Variable1 = x$var1,
    Variable2 = x$var2,
    Chi_Square = x$chi_square,
    P_Value = x$p_value,
    Cramers_V = x$cramer_v
  )
})) |>
  arrange(P_Value)

kable(results_df, 
      digits = 4,
      col.names = c("var1", "var2", "chi-statistic", "P-value", "Cramer's V"))
```
The correlation analysis of categorical variables in this breast cancer dataset reveals several key patterns. The strongest associations are found between staging-related variables, with differentiate-grade showing perfect correlation (Cramer's V = 1.0) and n_stage-x6th_stage displaying very strong correlation (Cramer's V = 0.91). A notable moderate correlation exists between hormone receptor statuses (estrogen_status-progesterone_status, Cramer's V = 0.51), which aligns with biological understanding. While many other associations are statistically significant (p < 0.05), their weaker Cramer's V values (< 0.3) suggest limited practical significance. 

#### Check the distribution of numerical variables
```{r}
surv_data |>
  funModeling::plot_num()
```
Box-Cox transformation
```{r}
surv_data = surv_data |>
  mutate(
      positive_ratio_transformed = {
      bc = boxcox(positive_ratio ~ 1, plotit = FALSE)
      lambda = bc$x[which.max(bc$y)]
      if(abs(lambda) < 1e-4) {
        log(positive_ratio)
      } else {
        (positive_ratio^lambda - 1) / lambda
      }
    }
  )
```

```{r}
p1 <- ggplot(surv_data, aes(x = positive_ratio)) +
  geom_histogram(fill = "skyblue", bins = 30) +
  labs(title = "Original Distribution",
       x = "Positive Ratio")

p2 <- ggplot(surv_data, aes(x = positive_ratio_transformed)) +
  geom_histogram(fill = "lightgreen", bins = 30) +
  labs(title = "Transformed Distribution",
       x = "Transformed Positive Ratio")

grid.arrange(p1, p2, ncol = 2)
```

## Model Building

### Kaplan-Meier Survival Analysis

Formula：

$$
\hat{S}(t) = \prod_{t_i \leq t} \left(1 - \frac{d_i}{n_i}\right)
$$

```{r}
survfit(Surv(survival_months,status)~race,data = surv_data) |> 
  ggsurvplot(
    size = 1,
    cex.lab= 2,
    break.time.by = 6,
    xlim = c(0,107),
    axis.title.x =element_text(size=5), 
    axis.title.y = element_text(size=5),
    palette = c("#54A136", "#C757A0", "#3291ca"),
    conf.int = TRUE,
    pval = TRUE,
    risk.table = TRUE,
    xlab = "Follow-up months", 
    ylab="Survival probability ",
    risk.table.col = "strata",
    risk.table.fontsize = 3, 
    legend.labs =  c("White", "Black", "Other" ),
    risk.table.height = 0.3, 
    ggtheme = theme_bw()
    )
```
```{r}
survfit(Surv(survival_months,status)~marital_status,data = surv_data) |> 
  ggsurvplot(
    size = 1,
    cex.lab= 2,
    break.time.by = 6,
    xlim = c(0,107),
    axis.title.x =element_text(size=5), 
    axis.title.y = element_text(size=5),
    palette = c("#54A136", "#C757A0", "#3291ca", "#FFA500", "#FF0000"),
    conf.int = TRUE,
    pval = TRUE,
    risk.table = TRUE,
    xlab = "Follow-up months", 
    ylab="Survival probability ",
    risk.table.col = "strata",
    risk.table.fontsize = 3, 
    legend.labs =  c("Married", "Single", "Separated", "Divored", "Widowed"),
    risk.table.height = 0.3, 
    ggtheme = theme_bw()
    )
```
```{r}
survfit(Surv(survival_months,status)~t_stage,data = surv_data) |> 
  ggsurvplot(
    size = 1,
    cex.lab= 2,
    break.time.by = 6,
    xlim = c(0,107),
    axis.title.x =element_text(size=5), 
    axis.title.y = element_text(size=5),
    palette = c("#54A136", "#C757A0", "#3291ca", "#FFA500", "#FF0000"),
    conf.int = TRUE,
    pval = TRUE,
    risk.table = TRUE,
    xlab = "Follow-up months", 
    ylab="Survival probability ",
    risk.table.col = "strata",
    risk.table.fontsize = 3, 
    legend.labs =  c("T1", "T2", "T3", "T4"),
    risk.table.height = 0.3, 
    ggtheme = theme_bw()
    )
```

```{r}
survfit(Surv(survival_months,status)~n_stage,data = surv_data) |> 
  ggsurvplot(
    size = 1,
    cex.lab= 2,
    break.time.by = 6,
    xlim = c(0,107),
    axis.title.x =element_text(size=5), 
    axis.title.y = element_text(size=5),
    palette = c("#54A136", "#C757A0", "#3291ca"),
    conf.int = TRUE,
    pval = TRUE,
    risk.table = TRUE,
    xlab = "Follow-up months", 
    ylab="Survival probability ",
    risk.table.col = "strata",
    risk.table.fontsize = 3, 
    legend.labs =  c("N1", "N2", "N3"),
    risk.table.height = 0.3, 
    ggtheme = theme_bw()
    )
```

```{r}
survfit(Surv(survival_months,status)~x6th_stage,data = surv_data) |> 
  ggsurvplot(
    size = 1,
    cex.lab= 2,
    break.time.by = 6,
    xlim = c(0,107),
    axis.title.x =element_text(size=5), 
    axis.title.y = element_text(size=5),
    palette = c("#54A136", "#C757A0", "#3291ca", "#FFA500", "#FF0000"),
    conf.int = TRUE,
    pval = TRUE,
    risk.table = TRUE,
    xlab = "Follow-up months", 
    ylab="Survival probability ",
    risk.table.col = "strata",
    risk.table.fontsize = 3, 
    legend.labs =  c("IIA", "IIB", "IIIA","IIIB", "IIIC"),
    risk.table.height = 0.3, 
    ggtheme = theme_bw()
    )
```

```{r}
survfit(Surv(survival_months,status)~differentiate,data = surv_data) |> 
  ggsurvplot(
    size = 1,
    cex.lab= 2,
    break.time.by = 6,
    xlim = c(0,107),
    axis.title.x =element_text(size=5), 
    axis.title.y = element_text(size=5),
    palette = c("#54A136", "#C757A0", "#3291ca", "#FFA500"),
    conf.int = TRUE,
    pval = TRUE,
    risk.table = TRUE,
    xlab = "Follow-up months", 
    ylab="Survival probability ",
    risk.table.col = "strata",
    risk.table.fontsize = 3, 
    legend.labs =  c("Moderately differentiated", "Poorly differentiated", "Well differentiated", "Undifferentiated"),
    risk.table.height = 0.3, 
    ggtheme = theme_bw()
    )
```

```{r}
survfit(Surv(survival_months,status)~grade,data = surv_data) |> 
  ggsurvplot(
    size = 1,
    cex.lab= 2,
    break.time.by = 6,
    xlim = c(0,107),
    axis.title.x =element_text(size=5), 
    axis.title.y = element_text(size=5),
    palette = c("#54A136", "#C757A0", "#3291ca", "#FFA500"),
    conf.int = TRUE,
    pval = TRUE,
    risk.table = TRUE,
    xlab = "Follow-up months", 
    ylab="Survival probability ",
    risk.table.col = "strata",
    risk.table.fontsize = 3, 
    legend.labs =  c("1", "2", "3", "4"),
    risk.table.height = 0.3, 
    ggtheme = theme_bw()
    )
```

```{r}
survfit(Surv(survival_months,status)~a_stage,data = surv_data) |> 
  ggsurvplot(
    size = 1,
    cex.lab= 2,
    break.time.by = 6,
    xlim = c(0,107),
    axis.title.x =element_text(size=5), 
    axis.title.y = element_text(size=5),
    palette = c("#54A136", "#C757A0"),
    conf.int = TRUE,
    pval = TRUE,
    risk.table = TRUE,
    xlab = "Follow-up months", 
    ylab="Survival probability ",
    risk.table.col = "strata",
    risk.table.fontsize = 3, 
    legend.labs =  c("Distant","Regional"),
    risk.table.height = 0.3, 
    ggtheme = theme_bw()
    )
```

```{r}
survfit(Surv(survival_months,status)~estrogen_status,data = surv_data) |> 
  ggsurvplot(
    size = 1,
    cex.lab= 2,
    break.time.by = 6,
    xlim = c(0,107),
    axis.title.x =element_text(size=5), 
    axis.title.y = element_text(size=5),
    palette = c("#54A136", "#C757A0"),
    conf.int = TRUE,
    pval = TRUE,
    risk.table = TRUE,
    xlab = "Follow-up months", 
    ylab="Survival probability ",
    risk.table.col = "strata",
    risk.table.fontsize = 3, 
    legend.labs =  c("Positive","Negative"),
    risk.table.height = 0.3, 
    ggtheme = theme_bw()
    )
```

```{r, message=FALSE}
survfit(Surv(survival_months,status)~progesterone_status,data = surv_data) |> 
  ggsurvplot(
    size = 1,
    cex.lab= 2,
    break.time.by = 6,
    xlim = c(0,107),
    axis.title.x =element_text(size=5), 
    axis.title.y = element_text(size=5),
    palette = c("#54A136", "#C757A0"),
    conf.int = TRUE,
    pval = TRUE,
    risk.table = TRUE,
    xlab = "Follow-up months", 
    ylab="Survival probability ",
    risk.table.col = "strata",
    risk.table.fontsize = 3, 
    legend.labs =  c("Positive","Negative"),
    risk.table.height = 0.3, 
    ggtheme = theme_bw()
    )
```

```{r}
surv_data = surv_data |>
  mutate(age_group = ifelse(age > mean(age, na.rm = TRUE), "Elder", "Young"))

survfit(Surv(survival_months,status)~age_group,data = surv_data) |>
  ggsurvplot(
    size = 1,
    cex.lab= 2,
    break.time.by = 6,
    xlim = c(0,107),
    axis.title.x =element_text(size=5), 
    axis.title.y = element_text(size=5),
    palette = c("#54A136", "#C757A0"),
    conf.int = TRUE,
    pval = TRUE,
    risk.table = TRUE,
    xlab = "Follow-up months", 
    ylab="Survival probability ",
    risk.table.col = "strata",
    risk.table.fontsize = 3, 
    legend.labs =  c("Young","Elder"),
    risk.table.height = 0.3, 
    ggtheme = theme_bw()
    )
```

```{r}
surv_data <- surv_data |>
  mutate(tumor_size_group = case_when(
    tumor_size < 40 ~ "Small (<40)",
    tumor_size >= 40 & tumor_size < 80 ~ "Medium (40-80)",
    tumor_size >= 80 & tumor_size < 120 ~ "Large (80-120)",
    tumor_size >= 120 ~ "Very Large (>120)"
  ))

 survfit(Surv(survival_months,status)~tumor_size_group,data = surv_data) |>
  ggsurvplot(
    size = 1,
    cex.lab= 2,
    break.time.by = 6,
    xlim = c(0,107),
    axis.title.x =element_text(size=5), 
    axis.title.y = element_text(size=5),
    palette = c("#54A136", "#C757A0", "#3291ca", "#FFA500"),
    conf.int = TRUE,
    pval = TRUE,
    risk.table = TRUE,
    xlab = "Follow-up months", 
    ylab="Survival probability ",
    risk.table.col = "strata",
    risk.table.fontsize = 3, 
    legend.labs =  c("Small (<40)", "Medium (40-80)", "Large (80-120)", "Very Large (>120)"),
    risk.table.height = 0.3, 
    ggtheme = theme_bw()
    )
```

```{r}
surv_data <- surv_data |>
  mutate(positive_ratio_group = case_when(
    positive_ratio <= 0.25 ~ "Low (0.02-0.25)",
    positive_ratio > 0.25 & positive_ratio <= 0.5 ~ "Moderate (0.25-0.5)",
    positive_ratio > 0.5 & positive_ratio <= 0.75 ~ "High (0.5-0.75)",
    positive_ratio > 0.75 ~ "Very High (0.75-1)"
  ))

 survfit(Surv(survival_months,status)~positive_ratio_group,data = surv_data) |>
  ggsurvplot(
    size = 1,
    cex.lab= 2,
    break.time.by = 6,
    xlim = c(0,107),
    axis.title.x =element_text(size=5), 
    axis.title.y = element_text(size=5),
    palette = c("#54A136", "#C757A0", "#3291ca", "#FFA500"),
    conf.int = TRUE,
    pval = TRUE,
    risk.table = TRUE,
    xlab = "Follow-up months", 
    ylab="Survival probability ",
    risk.table.col = "strata",
    risk.table.fontsize = 3, 
    legend.labs =  c("Low (0.02-0.25)", "Moderate (0.25-0.5)", "High (0.5-0.75)", "Very High (0.75-1)"),
    risk.table.height = 0.3, 
    ggtheme = theme_bw()
    )
```

All the Kaplan-Meier survival analyses show significant differences in survival probabilities among different groups of each variable.[ Log-rank test: p-value < 0.05]

The 'Number at risk' table below shows the decreasing number of patients available for follow-up over time in each risk group. This is expected as patients experience events (death) over time.

## Univariate Cox Regression Model

Formula:

$$
h(t) = h_0(t) \exp(\beta_1 X)
$$

```{r}
surv_object <- with(surv_data, Surv(survival_months, status))

result_unicox <- data.frame("Variable" = character(),
                     "Hazard Ratio" = numeric(),
                     "95%CI" = character(),
                     "P value" = numeric())

for (variable in c("age", "race", "marital_status", "t_stage", "n_stage", "x6th_stage", "differentiate", "grade", "a_stage", "tumor_size", "estrogen_status", "progesterone_status", "positive_ratio_transformed")) {
  cox_formula <- as.formula(paste("surv_object ~", variable))
  cox_model <- coxph(cox_formula, data = surv_data)
  
  variable_name <- variable
  hazard_ratio <- exp(coef(cox_model))
  ci_lower <- exp(confint(cox_model))[1]
  ci_upper <- exp(confint(cox_model))[2]
  p_value <- summary(cox_model)$coefficients[5]
  
  new_row <- data.frame("Variable" = variable_name,
                        "Hazard Ratio" = hazard_ratio,
                        "95% CI" = paste0("(", round(ci_lower, 2), "-", round(ci_upper, 2), ")"),
                        "P value" = p_value,
                        stringsAsFactors = FALSE)
  
  result_unicox <- rbind(result_unicox, new_row)
}

result_unicox = result_unicox |>
  arrange(desc(`P.value`))


knitr::kable(result_unicox, 
             col.names = c("Variable", "Hazard Ratio", "95% CI", "P value"))
```

According to the univariate Cox regression analysis, the variables `age,` `a_stage,` `tumor_size,` `grade,` `progesterone_status,` `estrogen_status,` and `positive_ratio`are significantly associated with the survival outcome (p < 0.05).

## Multivariate Cox Regression Model

Fomula:

$$
h(t|X) = h_0(t) \exp(\beta_1 X_1 + \beta_2 X_2 + \cdots + \beta_p X_p)
$$


```{r}
result_use = result_unicox |>
mutate(
  significant = ifelse(result_unicox$P.value < 0.05,"significant","Not significant"))

multi_cox <- result_use[result_use$significant == "significant",]$Variable

formula <- as.formula(paste("Surv(survival_months, status) ~", paste(multi_cox, collapse = " + ")))

multi_cox_model <- coxph(formula, data = surv_data)

data_use <- summary(multi_cox_model)

multi_cox_HR <- round(data_use$coefficients[,2],2)
multi_cox_CI2.5 <- round(data_use$conf.int[,3],2)
multi_cox_CI97.5 <- mul_CI95<-round(data_use$conf.int[,4],2)
multi_cox_CI <- paste0('(',multi_cox_CI2.5,'-',multi_cox_CI97.5,')')
multi_cox_P_value <- round(data_use$coefficients[,5],3)
Variable <- row.names(data.frame(data_use$coefficients))
multi_cox_result<- data.frame(Variable,multi_cox_HR,multi_cox_CI2.5,multi_cox_CI97.5,multi_cox_CI,multi_cox_P_value)

knitr::kable(multi_cox_result)
```

```{r, warning=FALSE}
ggplot(multi_cox_result, aes(multi_cox_HR, Variable)) + 
  geom_vline(xintercept = 1,
             linetype = "dashed",
             size = 1) +
  geom_errorbar(aes(xmin = multi_cox_CI2.5, xmax = multi_cox_CI97.5),width = 0.1) +
  geom_point(aes(color = multi_cox_P_value),size = 5, shape = 18) +
  scale_color_continuous(low = 'skyblue', high = 'red') +
  labs(x = 'Hazard ratio', title = 'Forest plot for multivariate cox regression') +
  theme_pubr() +
  theme(legend.position = 'right')
```

According to the multivariate Cox regression analysis, the variables `age,` `a_stage,` `tumor_size,` `grade,` `progesterone_status,` `estrogen_status,` and `positive_ratio` are significantly associated with the survival outcome (p < 0.05).

The forest plot also shows hazard ratios for various clinical factors in breast cancer. Notably, positive_ratio_transformed and grade demonstrated hazard ratios greater than 1 (approximately 1.5), indicating these factors are associated with increased risk. In contrast, progesterone_status Positive, estrogen_status Positive, and a_stage Regional showed hazard ratios less than 1 (around 0.5), suggesting these factors are protective. Both tumor_size and age had hazard ratios close to 1, indicating minimal impact on survival.

## Nomogram for Survival Prediction

```{r, warning=FALSE}
dd <- datadist(surv_data)
options(datadist = "dd")

surv_data = surv_data %>%
  mutate(survival_years = survival_months / 12)

surv_object <- with(surv_data, Surv(survival_years, status == 1))

final_model <- cph(surv_object ~ age + a_stage + tumor_size + grade + progesterone_status + estrogen_status + positive_ratio,
                   x = TRUE ,y = TRUE, surv = TRUE, data = surv_data)

surv =  Survival(final_model)

surv_1y <- function(x)surv(1,lp=x)
surv_4y <- function(x)surv(4,lp=x)
surv_8y <- function(x)surv(8,lp=x)

Nomogram_1 <- nomogram(final_model,fun = list(surv_1y,surv_4y,surv_8y),lp=F,
                       funlabel = c('1 year survival rate','4 year survival rate','8 year survival rate'),
                       maxscale = 100,fun.at = c(0.1,seq(0.1,0.9,by=0.1),0.90))

plot(Nomogram_1, 
     cex.axis = 0.4,
     cex.var = 0.8,
     cex = 0.8, 
     lmgp = 0.3,
     label.offset = 0.2,
     points.label = "Points",
     total.points.label = "Total Points",
     col.grid = gray(c(0.8, 0.95)),
     labels.right = FALSE,
     width.max = 1000,
     height.max = 800,
     mar = c(4, 4, 4, 4)
)
```
This nomogram predicts 1-year, 4-year, and 8-year survival rates for patients based on seven clinical variables: `age`, `a_stage`, `tumor_size`, `grade`, `progesterone_status`, `estrogen_status`, and `positive_ratio`.

To use this nomogram, points are assigned for each variable by drawing a vertical line up to the "Points" row. The sum of these points (Total Points) corresponds to the predicted survival probabilities at different time points. For example, a higher total points score indicates a poorer prognosis, with lower survival rates. The model incorporates both continuous variables and categorical variables (like hormone receptor status), providing a comprehensive risk assessment tool.

## ROC curve
```{r, warning=FALSE}
pred <- predict(final_model, type="lp")

ROC_table <- data.frame(time = surv_data[,"survival_years"], status = surv_data[,"status"], score = pred)

time_roc_res <- timeROC(T = ROC_table$survival_years,
                        delta = ROC_table$status,
                        marker = ROC_table$score,
                        cause = 1,
                        weighting="marginal",
                        times = c(1, 4, 8),
                        ROC = TRUE,
                        iid = TRUE
                        )

time_ROC_df <- data.frame(TP_1year = time_roc_res$TP[, 1],
                          FP_1year = time_roc_res$FP[, 1],
                          TP_4year = time_roc_res$TP[, 2],
                          FP_4year = time_roc_res$FP[, 2],
                          TP_8year = time_roc_res$TP[, 3],
                          FP_8year = time_roc_res$FP[, 3]
                          )

ggplot(data = time_ROC_df) +
  geom_line(aes(x = FP_1year, y = TP_1year), size = 1, color = "#0067B5") +
  geom_line(aes(x = FP_4year, y = TP_4year), size = 1, color = "#09891D") +
  geom_line(aes(x = FP_8year, y = TP_8year), size = 1, color = "#BC1328") +
  geom_abline(slope = 1, intercept = 0, color = "grey", size = 1, linetype = 2) +
  theme_bw() +
  annotate("text",x = 0.75, y = 0.20, size = 4.5,label = paste0("AUC of 1-year survival = ", sprintf("%.3f", time_roc_res$AUC[[1]])), color = "#0067B5") +
  annotate("text",x = 0.75, y = 0.15, size = 4.5,label = paste0("AUC of 4-year survival = ", sprintf("%.3f", time_roc_res$AUC[[2]])), color = "#09891D") +
  annotate("text",x = 0.75, y = 0.10, size = 4.5,label = paste0("AUC of 8-year survival = ", sprintf("%.3f", time_roc_res$AUC[[3]])), color = "#BC1328") +
  labs(x = "1-specificity", y = "Sensitivity") +
  theme(axis.text = element_text(face = "bold", size = 11, color = "black"),
        axis.title.x = element_text(face = "bold", size = 14, color = "black", margin = margin(c(15, 0, 0, 0))),
        axis.title.y = element_text(face = "bold", size = 14, color = "black", margin = margin(c(0, 15, 0, 0))))
```

This ROC (Receiver Operating Characteristic) curve displays the predictive performance of the model at different time points. The model shows good discriminative ability with AUC values of 0.764, 0.762, and 0.715 for 1-year, 4-year, and 8-year survival predictions, respectively.

The curves for all three time points are well above the diagonal reference line (gray dashed line), indicating better-than-random prediction. The similar AUC values for 1-year and 4-year predictions (0.764 and 0.762) suggest consistent model performance for shorter-term predictions, while there is a slight decrease in accuracy for long-term (8-year) predictions (AUC = 0.715).

## Calibration Curve

```{r, wearning=FALSE, message=FALSE}
surv_data = surv_data |>
  mutate(survival_days = survival_months * 30)

surv_object <- with(surv_data, Surv(survival_days, status == 1))

model_1 <- cph(surv_object ~ age + a_stage + tumor_size + grade + progesterone_status + estrogen_status + positive_ratio,
                   x = TRUE ,y = TRUE, surv = TRUE, time.inc = 365, data = surv_data)

cal_1 <- calibrate(model_1,
                   cmethod = 'KM',
                   method = 'boot',
                   u = 365,
                   B = 500)

plot(cal_1,
     lwd = 2,
     lty = 1,
     errbar.col="blue",
     xlab="Nomogram-Predicted Probabilityof 1 year OS",
     ylab="Actua1 1 year OS",
     col="red",
     subtitles=F
     )

abline(0, 1, lty = 2, col = "gray")
```


```{r, warning=FALSE, message=FALSE}
model_2 <- cph(surv_object ~ age + a_stage + tumor_size + grade + progesterone_status + estrogen_status + positive_ratio,
                   x = TRUE ,y = TRUE, surv = TRUE, time.inc = 4*365, data = surv_data)

cal_2 <- calibrate(model_2,
                   cmethod = 'KM',
                   method = 'boot',
                   u = 4*365,
                   B = 1000)

plot(cal_2,
     lwd = 2,
     lty = 1,
     errbar.col="blue",
     xlab="Nomogram-Predicted Probabilityof 4 years OS",
     ylab="Actua1 4 years OS",
     col="red",
     subtitles=F
     )

abline(0, 1, lty = 2, col = "gray")
```
```{r, warning=FALSE, message=FALSE}
model_3 <- cph(surv_object ~ age + a_stage + tumor_size + grade + progesterone_status + estrogen_status + positive_ratio,
                   x = TRUE ,y = TRUE, surv = TRUE, time.inc = 8*365, data = surv_data)

cal_3 <- calibrate(model_3,
                   cmethod = 'KM',
                   method = 'boot',
                   u = 8*365,
                   B = 1000)

plot(cal_3,
     lwd = 2,
     lty = 1,
     errbar.col="blue",
     xlab="Nomogram-Predicted Probabilityof 8 years OS",
     ylab="Actua1 8 years OS",
     col="red",
     subtitles=F
     )

abline(0, 1, lty = 2, col = "gray")
```


These three calibration plots demonstrate the performance of the nomogram in predicting overall survival (OS) at different time points (1-year, 4-year, and 8-year). The gray dashed lines represent perfect calibration, while the red lines show actual performance with blue confidence intervals.

For 1-year OS, the model shows excellent calibration with predicted probabilities ranging from 0.94 to 1.00. The 4-year OS predictions (0.6 to 0.9) and 8-year OS predictions (0.3 to 0.9) show good calibration but with wider confidence intervals and slightly more deviation from the ideal line. There is a noticeable trend across all three time points where the calibration accuracy decreases and uncertainty increases as the prediction time extends, which is expected in long-term survival predictions.

This suggests that the nomogram performs most reliably for short-term (1-year) predictions and maintains reasonable but decreasing accuracy for longer-term predictions.